---
title: "Comparing the characteristics of responses that resulted in a hospital transport to those that did not. Results from MedStar/Klarus MIH Program Data."
date: "Created: 2017-12-05 <br> Updated: `r Sys.Date()`"
output:
  word_document:
    reference_docx: word_style_template_01.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA)
Sys.setenv(TZ = "US/Central")
```

```{r load_packages, message=FALSE, echo=FALSE}
library(tidyverse)
library(feather)
library(bfuncs)
```

```{r echo=FALSE}
med_klar <- read_feather("../data/med_klar.feather")
# Created in data_preprocess_01.Rmd
```

All encounters used in this report where dated between `r min(med_klar$encounter)` and `r max(med_klar$encounter)`

# Analysis of transported

```{r echo=FALSE}
med_klar %>% 
  group_by(transported) %>% 
  freq_table()
```

The data includes information about 1,639 encounters. Overall, 999 (39%) encounters resulted in a transport and 640 (61%) did not.

```{r echo=FALSE}
med_klar %>% 
  group_by(mhp_on_scene, transported) %>% 
  freq_table()
```

At 83% of the encounters where there was no MHP on scene, the patient was transported to the hospital. Conversely, at 46% of the encounters where there was an MHP on scene, the patient was transported to the hospital.

# Table. Comparing the characteristics of responses that resulted in a hospital transport to those that did not.

```{r echo=FALSE}
# Create table shell
table <- tibble(
  variable = "",
  class    = "",
  no_trans = med_klar %>% bfuncs::get_group_n(transported == "No"),
  trans    = med_klar %>% bfuncs::get_group_n(transported == "Yes")
)


# Add statistics to column header
table <- bind_rows(
  table,
  tibble(
    variable = "",
    class    = "",
    no_trans = "n (Column %)",
    trans    = "n (Column %)"
  )
)


# Select variables
# ----------------
cat_vars  <- quos(mhp_on_scene, call_priority_r_f, encounter_type, ems_encounter_outcome)


# Fill in categorical variables
# -----------------------------
for (i in seq_along(cat_vars)) {
  
  # Calculate mean and 95% CI
  row <- med_klar %>% 
    group_by(transported, !!cat_vars[[i]]) %>% 
    freq_table() %>% 
    format_table(stats = "n and row percent") %>% 
    spread(key = transported, value = n_percent_row) %>% 
    mutate(variable = colnames(.)[1]) %>% 
    rename("class" = !!cat_vars[[i]], "no_trans" = `No`, "trans" = `Yes`) %>% 
    mutate(class = as.character(class)) # Need for bind_rows below
  
  # Append to bottom of table
  # Add a blank row after each variable
  # Blank lines mess up kable
  # blank_row <- tibble(
  #   variable = "",
  #   class    = "",
  #   no_trans = "",
  #   trans    = ""
  # )
  # 
  # if (i == 1) { # No blank betwee column header and first variable
  #   table <- bind_rows(table, row) 
  # } else {
  #   table <- bind_rows(table, blank_row, row)
  # }
  table <- bind_rows(table, row)
}


# Improve row headers
# -------------------
table <- table %>%
  mutate(
    variable = if_else(variable == "mhp_on_scene", "MHP on scene", variable),
    variable = if_else(variable == "call_priority_r_f", "Call priority", variable),
    variable = if_else(variable == "encounter_type", "Encounter type", variable),
    variable = if_else(variable == "ems_encounter_outcome", "Encounter outcome", variable)
  )

# Remove duplicate variable names for categorical variables
table <- table %>%
  group_by(variable) %>%
  mutate(
    x = duplicated(variable),
    x = if_else(variable == "", NA, x)
  ) %>%
  ungroup() %>%
  mutate(
    variable = if_else(x == TRUE, "", variable),
    variable = if_else(is.na(variable), "", variable),
    x = NULL
  )
```

```{r echo=FALSE}
# Knit to Kable
table_kable <- knitr::kable(table, col.names = c(
  "Characteristic",
  "Class",
  "Not Transported", 
  "Transported")
)

table_kable
```







