---
title: "Difference in Transported"
date: "Created: 2017-09-12 </br> `r Sys.Date()`"
output: html_notebook
---

```{r load_packages, message=FALSE}
# Load packages
library(tidyverse)
library(feather)
library(writexl)
```

## Import data

```{r}
medklar <- read_feather("../data/medklar.feather")
```


Are patients any more or less likely to be transported to the hospital when there is MHP/CCP intervention (on scene)?

* Primary exposure of interest: MHP on scene

* Primary outcome of interest: Transported to hospital

* Current data includes P1, P2, and P3 only

## Plot the data

```{r}

```

## Test for diffence

```{r}
trans_diff <- medklar %>% 
  group_by(mhp_on_scene, transported) %>% 
  summarise(
    Missing    = is.na(transported) %>% sum(),
    N          = n()
  ) %>% 
  mutate(
    CumSum     = cumsum(N),
    prop       = N / max(CumSum),
    se         = sqrt(prop * (1-prop) / (max(CumSum) - 1)),
    z          = qnorm(1 - 0.05 / 2),
    lcl        = prop - z * se,
    ucl        = prop + z * se,
    Percent    = prop * 100,
    `Lower CI` = lcl * 100,
    `Upper CI` = ucl * 100
  ) %>% 
  select(transported, mhp_on_scene, N, Percent,`Lower CI`, `Upper CI`)

trans_diff

# Put this code into R Notes
# Not exactly the same as Stata (after 4 digits) try SAS.
# Closely matches SAS as well, but not exactly. Different in CI's at 3rd digit.
# CI's get wider after accounting for clustering within person.
```

```{r}
gmodels::CrossTable(
  x = medklar$mhp_on_scene,
  y = medklar$transported,
  chisq = TRUE
)
```

Because some people appear in the data more than once, we need to test for a difference using a method that is robust to non-independence of observations. 

Doing in SAS first...

Export data

```{r}
write_xlsx(medklar, "/Users/bradcannell/Desktop/medklar.xlsx")
```



```{r session_info, echo=FALSE}
sessionInfo()
```